Structured Versus Decorated Cospans

### 2020-11-17 cospans.tex
changed \mathbf{D_0} to \lD_0, etc.

This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $F \mathbf{Csp} \mapseqq H(F \lCsp)$ as the `horizontal edge bicategory' of the double category $F \mathbb{C}$sp. This bicategory $F \mathbf{Csp}$ has:
\begin{enumerate}
\item{objects as those of $\mathrm{A}$,}
\item{morphisms as the horizontal 1-cells of $F\mathbb{C}$sp, which are $F$-decorated cospans of $\A$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,0) {$b$};
\node (C) at (2,0) {$a_2$};
\node (D) at (3,0) {$d \in F(b)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms as maps of $F$-decorated cospans in $\A$ with the same feet together with a natrual transformation.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$b$};
\node (B') at (1,-1) {$b'$};
\node (C) at (2,0) {$a_2$};
\node (D) at (3,0) {$1$};
\node (E) at (4,0.5) {$F(b)$};
\node (E') at (4,-0.5) {$F(b')$};
\node (F) at (3.65,0) {$\Swarrow \tau$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i'$} (B')
(C) edge node[below]{$o'$} (B')
(B) edge node [left] {$f$} (B')
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d'$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
}
\end{enumerate}
This bicategory $F\mathbf{Csp}$ is superior to the original bicategory $F$Cospan$(A)$ constructed by the second author \cite{Courser} in that it has the 2-morphisms that one would expect such a bicategory to have, such as (\ref{no2morphism}).

@@

\begin{thm} \label{thm:equiv}
Suppose $\ca{A}$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor. Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are equivalent, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
\end{thm}

@@

Notice a subtlety in the above formulation: \cref{lem:MonGroth} provides a specifically induced monoidal structure on the fibres which becomes \cref{eq:explicitstructure1} in the cocartesian base case. If that fibrewise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to \emph{any} other cocartesian structure on the fibres, by universal property of colimits. Therefore, we can simplify the above formulation to the one of the very \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor. DOES THIS MAKE SENSE TO ALL??

On a highly related note, in what follows we are also interested in the existence of a left adjoint $L_F$ to an induced monoidal opfibration; the following result provides sufficient conditions for that.

@@

Finally, if the original pseudofunctor is in fact lax monoidal $(F,\mu,\mu_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
\begin{equation}\label{eq:initialinfibre}
\mathbf{1}\xrightarrow{\mu_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
\end{equation}
\end{rmk}

@@

\begin{defn}
Given a set $\La$ of \define{labels}, an $\La$-\define{graph} is a graph $s,t\maps E\to N$
 equipped with a function $\ell \maps E \to \La$.
 A \define{morphism} from the $\La$-graph 
 \[ \xymatrix{\La & E \ar@<2.5pt>[r]^{s} \ar@<-2.5pt>[r]_{t} \ar[l]_{\ell} & N} \]
 to the $\La$-graph 
\[ \xymatrix{\La & E' \ar@<2.5pt>[r]^{s'} \ar@<-2.5pt>[r]_{t'} \ar[l]_{\ell'} & N'} \]
is a pair of functions $f \maps E \to E', g \maps N \to N'$ such that these diagrams commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$E$};
\node (A') at (0,-1) {$E'$};
\node (B) at (1,0) {$N$};
\node (B') at (1,-1) {$N'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$s$} (B)
(A') edge node[above]{$s'$} (B')
(A) edge node[left]{$f$} (A')
(B) edge node[right]{$g$} (B');

@@

When $\La = 1$, an $\La$-graph reduces to a graph and $\Graph_\La$ reduces
to the category $\Graph$ discussed in \cref{subsec:graphs}.  We now generalize the key
ideas of that section from graphs to $\La$-graphs.   Everything works the same way, 
but following previous work \cite{BCR} we call an open $\La$-graph an $\La$-\define{circuit}.

There is a functor $U \maps \Graph_\La \to \Fin\Set$ that takes an $\La$-graph to its underlying set of nodes. This has a left adjoint $L \maps \Fin\Set \to \Graph_\La$ sending
any set to the $\La$-graph with that set of nodes and no edges.  Both $\Fin\Set$ and $\Graph_\La$ have colimits, and $L$ preserves them.  Thus \cref{SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where:
\begin{itemize}
\item an object is a finite set,
\item a morphism is an isomorphism class of $\La$-circuits, where an
$\La$-\define{circuit} is a cospan in $\Graph_\La$ of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(S)$};
\node (B) at (1,0) {$G$};
\node (C) at (2,0) {$L(T)$,};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above,left]{$$} (B)
(C)edge node[above]{$$}(B);
\end{tikzpicture}
\]
and an \define{isomorphism} of $\La$-circuits is a commutative diagram in $\Graph_\La$ 
of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (E) at (3,-0.5) {$L(S)$};
\node (F) at (5,-0.5) {$L(T)$};
\node (G) at (4,0) {$G$};
\node (G') at (4,-1) {$G'$};
\path[->,font=\scriptsize,>=angle 90]
(F) edge node[above]{$o$} (G)
(G) edge node[left]{$h$} (G')
(E) edge node[above]{$i$} (G)
(E) edge node[below]{$i'$} (G')
(F) edge node[below]{$o'$} (G');
\end{tikzpicture}
\]
where $h$ is an isomorphism.
\end{itemize} 
This category has a nice universal property, found by Rosebrugh, Sabadini and
Walters \cite{RSW}.  To state this, it is convenient to use the language of props.
% Replaced strict symmetric with symmetric strict three times below
Recall that a \define{prop} is a symmetric strict monoidal category whose objects are natural
numbers, with tensor product of objects given by addition.  An \define{algebra} of a prop $\T$ in a symmetric strict monoidal category $\C$ is a symmetric strict monoidal functor $A \maps \T \to \C$.   A \define{morphism} from the algebra $A \maps \T \to \C$ to the algebra
$A' \maps \T \to \C$ is a monoidal natural transformation $\alpha \maps A \To A'$.

@@

\subsection{Double categories}\label{sec:doublecats}
%!!! Christina: Kenny, would you mind cleaning this section up to? I don't believe we need the full fledged definitions here by the way.

Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:

\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]

We call $A, B, C$ and $D$ \textbf{objects} or \textbf{0-cells}, $f$ and $g$ \textbf{vertical 1-morphisms}, $M$ and $N$ \textbf{horizontal 1-cells} and $a$ a \textbf{2-morphism}. Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells. We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'. We follow the notation of Shulman \cite{Shulman2008} with the following definitions.

\begin{defn}\label{defn:double_category}
A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\mathbf{D_{0}}$ and a category of arrows $\mathbf{D_1}$ with the following functors
\begin{center}
$U\maps \mathbf{D_{0}} \to \mathbf{D_1}$\\
$S,T \maps \mathbf{D_1} \rightrightarrows \mathbf{D_{0}}$\\
$\odot \maps \mathbf{D_1} \times_{\mathbf{D_{0}}} \mathbf{D_1} \to \mathbf{D_1}$ (where the pullback is taken over $\mathbf{D_1} \xrightarrow[]{T} \mathbf{D_{0}} \xleftarrow[]{S} \mathbf{D_1}$) \\
\end{center}
 such that \\
\begin{center}
$S(U_{A})=A=T(U_{A})$\\
$S(M \odot N)=SN$\\
$T(M \odot N)=TM$\\
\end{center}
equipped with natural isomorphisms
\begin{center}

@@

\end{center}
such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied. Following the notation of Shulman, objects of $\mathbf{D_{0}}$ are called $\textbf{0-cells}$ and morphisms of $\mathbf{D_{0}}$ are called $\textbf{vertical 1-morphisms}$. Objects of $\mathbf{D_1}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\mathbf{D_1}$ are called $\textbf{2-morphisms}$. The morphisms of $\mathbf{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$. Then a 2-morphism $a \maps M \to N$ of $\mathbf{D_1}$ with $S(a)=f,T(a)=g$ would look like:
\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]
\end{defn}

The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism. Equivalently, as a double category can be viewed as a category internal to $\Cat$, we can view a pseudo double category as a category `weakly' internal to $\Cat$. We will sometimes omit the word pseudo and simply say double category.

\begin{defn}
A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
\end{defn}

\begin{defn}
Let $\lD$ be a pseudo double category. Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
\end{defn}

@@

\item $\mathbf{D_{0}}$ and $\mathbf{D_1}$ are both monoidal categories.
\item If $I$ is the monoidal unit of $\mathbf{D_{0}}$, then $U_I$ is the
  monoidal unit of $\mathbf{D_1}$.

>>>>

This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $F \mathbf{Csp}$ as the `horizontal bicategory' of the double category $F \mathbb{C}$sp. This bicategory $F \mathbf{Csp}$ has:
\begin{enumerate}
\item{objects as those of $\mathrm{A}$,}
\item{morphisms as the horizontal 1-cells of $F\mathbb{C}$sp, which are $F$-decorated cospans of $\A$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,0) {$b$};
\node (C) at (2,0) {$a_2$};
\node (D) at (3,0) {$d \in F(b)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms as maps of $F$-decorated cospans in $\A$ with the same feet together with a natrual transformation.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$b$};
\node (B') at (1,-1) {$b'$};
\node (C) at (2,0) {$a_2$};
\node (D) at (3,0) {$1$};
\node (E) at (4,0.5) {$F(b)$};
\node (E') at (4,-0.5) {$F(b')$};
\node (F) at (3.65,0) {$\Swarrow \tau$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i'$} (B')
(C) edge node[below]{$o'$} (B')
(B) edge node [left] {$f$} (B')
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d'$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
}
\end{enumerate}
This bicategory $F\mathbf{Csp}$ is superior to the original bicategory $F$Cospan$(A)$ constructed by the second author \cite{Courser} in that it has the 2-morphisms that one would expect such a bicategory to have, such as (\ref{no2morphism}).

@@

\begin{thm} \label{thm:equiv}
Suppose $\A$ has finite colimits and $F \maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.   Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
\end{thm}

@@

On a highly related note, in what follows we are also interested in the existence of a left adjoint $L_F$ to an induced monoidal opfibration; the following result provides sufficient conditions for that.
%, which go hand-in-hand with \cref{cor:fcocMonGroth} and \cref{lem:fibrewiselimits}.

@@

Finally, if the original pseudofunctor is in fact lax monoidal $(F,\mu,\mu_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
\begin{equation}\label{eq:initialinfibre}
\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
\end{equation}
\end{rmk}

@@

\begin{defn}
Given a set $\La$ of \define{labels}, an \define{$\La$-graph} is a graph $s,t\maps E\to N$
 equipped with a function $\ell \maps E \to \La$.
 A \define{morphism} from the $\La$-graph 
 \[ \xymatrix{\La & E \ar@<2.5pt>[r]^{s} \ar@<-2.5pt>[r]_{t} \ar[l]_{\ell} & N} \]
 to the $\La$-graph 
\[ \xymatrix{\La & E' \ar@<2.5pt>[r]^{s'} \ar@<-2.5pt>[r]_{t'} \ar[l]_{\ell'} & N'} \]
is a pair of functions $f \maps E \to E', g \maps N \to N'$ such that these diagrams commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$E$};
\node (A') at (0,-1) {$E'$};
\node (B) at (1,0) {$N$};
\node (B') at (1,-1) {$N'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$s$} (B)
(A') edge node[above]{$s'$} (B')
(A) edge node[left]{$f$} (A')
(B) edge node[right]{$g$} (B');

@@

When $\La = 1$, an $\La$-graph reduces to a graph and $\Graph_\La$ reduces
to the category $\Graph$ discussed in \cref{subsec:graphs}.  We now generalize the key
ideas of that section from graphs to $\La$-graphs.   Everything works the same way, 
but following previous work \cite{BCR} we call an open $\La$-graph an \define{$\La$-circuit}.

There is a functor $U \maps \Graph_\La \to \Fin\Set$ that takes an $\La$-graph to its underlying set of nodes. This has a left adjoint $L \maps \Fin\Set \to \Graph_\La$ sending
any set to the $\La$-graph with that set of nodes and no edges.  Both $\Fin\Set$ and $\Graph_\La$ have colimits, and $L$ preserves them.  Thus \cref{SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where:
\begin{itemize}
\item an object is a finite set,
\item a morphism is an isomorphism class of $\La$-circuits, where an
\define{$\La$-circuit} is a cospan in $\Graph_\La$ of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(S)$};
\node (B) at (1,0) {$G$};
\node (C) at (2,0) {$L(T)$,};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above,left]{$$} (B)
(C)edge node[above]{$$}(B);
\end{tikzpicture}
\]
and an \define{isomorphism} of $\La$-circuits is a commutative diagram in $\Graph_\La$ 
of this form:
\[
\begin{tikzpicture}[scale=1.5]
\node (E) at (3,-0.5) {$L(S)$};
\node (F) at (5,-0.5) {$L(T)$};
\node (G) at (4,0) {$G$};
\node (G') at (4,-1) {$G'$};
\path[->,font=\scriptsize,>=angle 90]
(F) edge node[above]{$o$} (G)
(G) edge node[left]{$h$} (G')
(E) edge node[above]{$i$} (G)
(E) edge node[below]{$i'$} (G')
(F) edge node[below]{$o'$} (G');
\end{tikzpicture}
\]
where $h$ is an isomorphism.
\end{itemize} 
This category has a nice universal property, found by Rosebrugh, Sabadini and
Walters \cite{RSW}.  To state this, it is convenient to use the language of props.
% Replaced strict symmetric with symmetric strict three times below
Recall that a \define{prop} is a symmetric strict monoidal category whose objects are natural
numbers, with tensor product of objects given by addition.  An \define{algebra} of a prop $\T$ in a symmetric strict monoidal category $\C$ is a symmetric strict monoidal functor $A \maps \T \to \C$.   A \define{morphism} from the algebra $A \maps \T \to \C$ to the algebra
$A' \maps \T \to \C$ is a monoidal natural transformation $\alpha \maps A \To A'$.

@@

\subsection{Double categories}\label{sec:doublecats}

Before formally defining a `double category', it is helpful to have the following picture in mind. A double category has 2-morphisms shaped like:
\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]
We call $A, B, C$ and $D$ \textbf{objects}, $f$ and $g$ \textbf{vertical 1-morphisms}, $M$ and $N$ \textbf{horizontal 1-cells} and $a$ a \textbf{2-morphism}. Note that a vertical 1-morphism is a morphism between objects and a 2-morphism is a morphism between horizontal 1-cells. %We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'. 
We follow the notation of Shulman \cite{Shulman2008} with the following definitions.

\begin{defn}\label{defn:double_category}
A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\lD_0$ and a category of arrows $\lD_1$ with the following functors
\begin{center}
$U\maps \lD_0 \to \lD_1$\\
$S,T \maps \lD_1 \rightrightarrows \lD_0$\\
$\odot \maps \lD_1 \times_{\lD_0} \lD_1 \to \lD_1$ (where the pullback is taken over $\lD_1 \xrightarrow[]{T} \lD_0 \xleftarrow[]{S} \lD_1$) \\
\end{center}
 such that \\
\begin{center}
$S(U_{A})=A=T(U_{A})$\\
$S(M \odot N)=SN$\\
$T(M \odot N)=TM$\\
\end{center}
equipped with natural isomorphisms
\begin{center}

@@

\end{center}
such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied. Following the notation of Shulman, objects of $\lD_0$ are called $\textbf{0-cells}$ and morphisms of $\lD_0$ are called $\textbf{vertical 1-morphisms}$. Objects of $\lD_1$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\lD_1$ are called $\textbf{2-morphisms}$. The morphisms of $\lD_1$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$. Then a 2-morphism $a \maps M \to N$ of $\lD_1$ with $S(a)=f,T(a)=g$ would look like:
\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]
\end{defn}
A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.

%The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism. Equivalently, as a double category can be viewed as a category internal to $\Cat$, we can view a pseudo double category as a category `weakly' internal to $\Cat$. We will sometimes omit the word pseudo and simply say double category.

%\begin{defn}
%Let $\lD$ be a pseudo double category. Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
%\end{defn}

@@

\item $\lD_0$ and $\lD_1$ are both monoidal categories.
\item If $I$ is the monoidal unit of $\lD_0$, then $U_I$ is the
  monoidal unit of $\lD_1$.
